% resume.tex
% Credit for this template goes to Jeremy Edberg
% Jarrid Rector-Brooks <jrectorb@umich.edu> 2018

%%%%%%%%%%%%
% Basic setup
\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{setspace}
\pagestyle{empty}
\setlength{\tabcolsep}{0in}
\hyphenchar\font=-1
\usepackage{geometry} 
\geometry{a4paper, twoside} 
\setstretch{1}
\usepackage{booktabs}
\usepackage{topcapt}
%\raggedbottom
%\raggedright
\usepackage{tabulary}
\usepackage{hyphenat}
\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
%%%%%%%%%%%%

%%%%%%%%%%%%
% PDF setup
\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{hyperref}
  \makeatletter\let\@bibitem\saved@bibitem\makeatother
\else
  \usepackage[hypertex]{hyperref}
  \makeatletter\let\@bibitem\saved@bibitem\makeatother
\fi
\hypersetup{
    letterpaper,
    colorlinks,
    urlcolor=black,
    pdfpagemode=none,
    pdftitle={Resume},
    pdfauthor={Jarrid Rector-Brooks},
    pdfsubject={Resume},
    pdfkeywords={
        Artificial Intelligence, Optimization, Systems, Facebook, Microsoft,
        Akuna Capital, Distributed Systems, Profiling Tools, mParticle
    }
}
%%%%%%%%%%%%

%%%%%%%%%%%%
% Margin setup
\oddsidemargin  -0.5in
\evensidemargin -0.5in
\textwidth      7.2in
\headheight     -0.7in
\topmargin      0.0in
\textheight=10.7in
%\footheight 1.0in 
%%%%%%%%%%%%

\begin{document}

%% Bib setup
\nobibliography{JarridRectorBrooksResume}
\bibliographystyle{ieeetr}

%% Heading
\begin{center}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr}
    &\huge{\textbf{\sc{Jarrid Rector-Brooks}}}&\\
    &&\\
    Email: jarridrb@gmail.com & Github: \url{https://github.com/jarridrb} & Mobile: (517) 798-7394\\
\hline\hline
\end{tabular*}
\end{center}

%% Education Section
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Education}}\\
\hline
\end{tabular*}

%% UdeM PhD
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Universit\'e de Montr\'eal, Mila} & \emph{September 2021 - Present} \\
\emph{PhD in Computer Science, Advised by Yoshua Bengio}  \\
\end{tabular*}
{\small

\noindent

\begin{list}{$\bullet$}{
%\setlength{\itemsep}{ -5pt}
%\setlength{\partopsep}{ -18pt}
}
\item \underline{Courses:} Probabilistic Graphical Models, Reinforcement Learning, Representation Learning, Theoretical Principles for Deep Learning, Geometry and Generative Models, Dynamical Systems
\item \underline{GPA:} 4.14 / 4.00

\end{list}
}

%% UMich B.Sc.
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{University of Michigan -- Ann Arbor} & \emph{September 2013 - December 2017} \\
\emph{Bachelor's of Science in Computer Science with Honors}  \\
\end{tabular*}
{\small

\noindent

\begin{list}{$\bullet$}{
%\setlength{\itemsep}{ -5pt}
%\setlength{\partopsep}{ -18pt}
}
\item \underline{Thesis:} ``Using Profiling to Analyze Latency Variance''
\item \underline{Relevant Courses:} Discrete Mathematics, Data Structures and 
                                    Algorithms, Introduction to Computer Organization, 
                                    Operating Systems, Web Databases and Information 
                                    Systems, Machine Learning, Distributed Systems
\item \underline{GPA:} 3.63 / 4.00

\end{list}
}

%% Publications
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Publications}}\\
\hline
\end{tabular*}
\\

\noindent 
\bibentry{rector2024steering} \\ \\
\bibentry{berner2025discrete} \\ \\
\bibentry{kim2024adaptive} \\ \\
\bibentry{sendera2024improved} \\ \\
\bibentry{venkatraman2025amortizingintractableinferencediffusion} \\ \\
\bibentry{huguet2024sequence} \\ \\
\bibentry{korablyov2024generativeactivelearningsearch} \\ \\
\bibentry{akhound2024iterated} \\ \\
\bibentry{sendera2024diffusion} \\ \\
\bibentry{govindarajan2024learning} \\ \\
\bibentry{bose2023se} \\ \\
\bibentry{jain2023multi} \\ \\
\bibentry{madan2023learning} \\ \\
\bibentry{rector2023thompson} \\ \\
\bibentry{tong2023improving} \\ \\
\bibentry{govindarajan2023behavioral} \\ \\
\bibentry{levy2023molecular} \\ \\
\bibentry{jain2022bioseqdesign} \\ \\
\bibentry{bertin2022recover} \\ \\
\bibentry{jain2021deup} \\ \\
\bibentry{myFWPaper}

%% Community Service
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Community Service}}\\
\hline
\end{tabular*}

%% ICLR 2025 GEM Workshop
\noindent
\\
\textbf{Organizer for ICLR 2025 Workshop on Generative and Experimental Perspectives for Biomolecular Design} \\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    Singapore, Singapore & \emph{May 2025} \\
\end{tabular*}

%% Mila/KAIST Prefrontal AI Workshop 2024
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Organizer for KAIST-Mila Prefrontal AI Workshop} & \\
    Montr\'eal, Canada & \emph{December 2024} \\
\end{tabular*}

%% ICLR 2024 GEM Workshop
\noindent
\\
\textbf{Organizer for ICLR 2024 Workshop on Generative and Experimental Perspectives for Biomolecular Design}  \\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    Vienna, Austria & \emph{May 2024} \\
\end{tabular*}

%% Work Experience Section
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Work Experience}}\\
\hline
\end{tabular*}

%% Dreamfold Co-Founder
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Dreamfold, Co-Founder}, Montr\'eal, QC, Canada & \emph{October 2021 to October 2024} \\
\end{tabular*}
{\small

\noindent
\begin{itemize}
    \item Helped to build and publish multiple state-of-the-art protein generative models in FoldFlow-1 and FoldFlow-2.
    \item Built company profile by leading organization of ICLR 2024 Generative and Experimental Perspectives for Biomolecular Design workshop.
    \item Raised over \$6 million USD.
\end{itemize}
}

%% mParticle Machine Learning Engineer
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{mParticle, Senior Machine Learning Engineer}, New York, NY, USA & \emph{May 2019 to September 2021} \\
\emph{Data Science Team} 
\end{tabular*}
{\small

\noindent
\begin{itemize}
    \item Helped build and maintain data pipelines processing over eight and a half billion events daily while maintaining average query latencies below 500 milliseconds.
    \item Built infrastructure to efficiently, accurately, and correctly estimate various population statistics for extremely high cardinality sets.
    \item Supervised project to create pre-built, usable models for running within data warehouses.
    \item Created and ran internal reading group (focusing on Statistical Learning Theory and Distributed Computing Theory).
\end{itemize}
}

%% UMich Research Assistant
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Research Associate}, Ann Arbor, MI, USA & \emph{January 2017 to February 2019} \\
\emph{Fully Autonomous \& Infinitely Scalable Lab, Advised by Professor Barzan Mozafari} 
\end{tabular*}
{\small

\noindent
\begin{itemize}
    \item Wrote and published a paper in AAAI-19 deriving new, state-of-the-art convergence rates for the Frank-Wolfe algorithm.
    \item Helped build and open source a profiler (VProfiler) which measures root causes of variance for an arbitrary software system (given the system is written in C or C++).
    \item VProfiler found issues deep within MySQL\@.  Through this discovery, changes were made to MySQL which are now included in all MySQL distributions and default on MariaDB distributions, impacting over 2 million installations worldwide.
    \item Built a novel search engine enabling declarative travel.
\end{itemize}
}

%% Facebook Internship
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Facebook, Software Engineering Intern}, Menlo Park, CA, USA & \emph{May 2017 to August 2017} \\
\emph{Ads Ranking Team} 
\end{tabular*}
{\small

\noindent
\begin{itemize}
    \item Built tool for automated model selection.
    \item Built tool which automated augmentation of various types of features.
    \item Ran an internal machine learning reading group.
\end{itemize}
}

%% Microsoft Internship
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Microsoft, Software Engineering Intern}, Sunnyvale, CA, USA & \emph{May 2016 to August 2016} \\
\emph{Serving Team, Bing Product Ads Division} 
\end{tabular*}
{\small

\noindent
\begin{itemize}
    \item Collaborated with Microsoft Research developing logging systems in C++ and C\# leveraging  
          Event Tracing for Windows to enable enhanced management of large scale log data.
    \item Created a UI utilizing AngularJS and Vega-Lite to provide easy trend analysis of log data.
\end{itemize}
}

%% Akuna Internship
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Akuna Capital, Software Engineering Intern}, Chicago, IL, USA & \emph{May 2015 to August 2015} \\
\emph{Trading Engine Team} 
\end{tabular*}
{\small

\noindent
\begin{itemize}
    \item Built configuration manager which generates, optimizes, and enforces invariants on trading engine configurations.
\end{itemize}
}

%% Invited Talks Section
%\noindent
%\\
%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
%\large {\sc {Invited Talks}}\\
%\hline
%\end{tabular*}

%% Skills
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Skills}}\\
\hline
\end{tabular*}

\begin{description}
    \item[Programming Languages:] \hfill \\
        {\small C++, C, C\#, Python, Javascript, Go, Java, MATLAB, \LaTeX}

    \item[Operating Systems:] \hfill \\
        {\small Linux/Unix, OS X, Windows}

    \item[Frameworks \& Technologies:] \hfill \\
        {\small
            PyTorch, Ray, RlLib, Vim, Git, MapReduce, Hive, .NET Core, .NET Framework, CPlex, 
            Celery, Django, SQL, HQL, LLVM, NumPy, SciPy, Sklearn, Apache HTTP Server, 
            Apache Druid, AWS
        }

\end{description}

\end{document}
